---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vCardR

<!-- badges: start -->
<!-- badges: end -->

The goal of vCardR is to generate `*.vcf`-format contact book in batch.

## Installation

You can install the development version of vCardR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("gaospecial/vCardR")
```

```{r include=FALSE}
data = data.frame(
  name = c("Tom","Jack"),
  cell = c("13033339999","13800000000"),
  org = c("Google","Baidu")
)
write.csv(data, file = "inst/extdata/contact.csv", row.names = F)
```


## Example

Suppose we have a data sheet with several entries.

```{r}
file = system.file("extdata", "contact.csv", package = "vCardR")
contact_book = read.csv(file)
contact_book
```

Build VCARD for every person.

```{r}
library(dplyr)
library(vCardR)
vcf = contact_book %>% 
  rowwise() %>% 
  mutate(vcard = vcard(name = name, cell = cell, org = org)) %>% 
  pull(vcard)
```

And write the contact list to a `vcf` file using `xfun::write_utf8()`.

```{r eval=FALSE}
xfun::write_utf8(vcf, "contact.vcf")
```

Now, the `vcf` file can be easily imported into smartphone contact list.
